Canopy leaf area of a mature evergreen *Eucalyptus* woodland does not respond to elevated atmospheric [CO~2~] but tracks water availability

### 2015-05-26 manuscript.Rmd
caption fixes

**Figure 1**. (a) Target [CO~2~] (C~a~) relative to the ambient C~a~ treatment at the EucFACE. The elevated C~a~ treatment proceeded in steps of 30 ppm, reaching +150 ppm in February 2013. (b) Canopy transmittance ($\tau_d$) estimated from continuous time series of photosynthetically active radition (PAR) below and above the canopy, for highly diffuse conditions (F~diff~ > 0.98) only. The solid lines are smoothed time series (with 95% confidence intervals) for each FACE ring (using a generalized additive model). Lines in blue colours denote ambient C~a~ treatment, red colours are elevated C~a~ (+150 ppm). Note the steep increase in $\tau_d$ for Ring 6 around November 2014, due to an insect attack that resulted in near defoliation of the canopy. The arrow labelled ‘calibration’ indicates a drought period when $\tau_d$ steadily increased, used to calibrate *L* estimates to litter production (see Methods).

@@

**Figure 6**.  (a) Total litter production (converted from data in Fig. 5 to an annual estimate) for each of the FACE rings plotted against mean $L_\tau$ during the entire litter collection period. The ratio of mean $L_\tau$ to annual litter production gives the mean leaf life span. Grey lines indicate leaf lifespan isolines. (b) Calculated leaf lifespan for the six FACE rings shows a significant difference between C~a~ treatments (p `r pval(LLtest$p.value)`).

>>>>

**Figure 1**. (a) Target [CO~2~] (C~a~) relative to the ambient C~a~ treatment at the EucFACE. The elevated C~a~ treatment proceeded in steps of 30 ppm, reaching +150 ppm in February 2013. (b) Canopy transmittance ($\tau_d$) estimated from continuous time series of photosynthetically active radition (PAR) below and above the canopy, for highly diffuse conditions (F~diff~ > 0.98) only. The solid lines are smoothed time series (with 95% confidence intervals) for each FACE ring (using a generalized additive model). Lines in blue colours denote ambient C~a~ treatment, red colours are elevated C~a~. Note the steep increase in $\tau_d$ for Ring 6 around November 2014, due to an insect attack that resulted in near defoliation of the canopy. The arrow labelled ‘calibration’ indicates a drought period when $\tau_d$ steadily increased, used to calibrate *L* estimates to litter production (see Methods).

@@

**Figure 6**.  (a) Total litter production (converted from data in Fig. 5 to an annual estimate) for each of the FACE rings plotted against mean $L_\tau$ during the entire litter collection period. The ratio of mean $L_\tau$ to annual litter production gives the mean leaf life span. Grey lines indicate leaf lifespan isolines (in years). (b) Calculated leaf lifespan for the six FACE rings shows a significant difference between C~a~ treatments (t-test, p `r pval(LLtest$p.value)`).
